\section{Hamiltonian, Eigenstates and Matrix Notation}

To start out, we will consider two eigenstates $\ket{\varphi_1}$, $\ket{\varphi_2}$ of the Hamiltonian $\hat{H}_0$ with
\begin{align}
 \hat{H}_0\ket{\varphi_1}=E_1\ket{\varphi_1}, \qquad \hat{H}_0\ket{\varphi_2}=E_2\ket{\varphi_2}.
\end{align}
Quite typically we might think of it as a two-level atom with states 1 and 2. The eigenstates can be expressed in matrix notation:
\begin{align}
 \ket{\varphi_1}=\left( \begin{array}{c} 1 \\ 0 \end{array} \right), \qquad \ket{\varphi_2}=\left( \begin{array}{c} 0 \\ 1 \end{array} \right),
\end{align}
so that $\hat{H}_0$ be written as a diagonal matrix
\begin{align}
    \hat{H}_0 = \left(\begin{array}{cc} E_1 & 0 \\ 0 & E_2 \end{array}\right).
\end{align}
If we would only prepare eigenstates the system would be rather boring. However, we typically have the ability to change the Hamiltonian by switching on and off laser or microwave fields \footnote{See the discussions of the next lecture}. We can then write the Hamiltonian in its most general form as:
\begin{align}\label{Eq:TwoLevelGeneral}
\hat{H} = \frac{\hbar}{2}\left( \begin{array}{cc} \Delta  & \Omega_x - i\Omega_y\\ \Omega_x +i\Omega_y & -\Delta \end{array} \right)
\end{align}
Sometimes we will also chose the definition:
\begin{align}
\Omega = |\Omega| e^{i\varphi}=\Omega_x + i\Omega_y
\end{align}
It is particularly useful for the case in which the coupling is created by a laser. Another useful way of thinking about the two-level system is as a spin in a magnetic field. 

We can also employ the definition of the spin-1/2 matrices to rewrite the Hamiltonian as:

ADD THE SPIN LANGUAGE
\begin{align}
s_x = \frac{\hbar}{2}\left(\begin{array}{cc}
0 & 1\\
1 &  0
\end{array}
\right)~
s_y = \frac{\hbar}{2}\left(\begin{array}{cc}
0 & -i\\
i &  0
\end{array}
\right)~s_z =\frac{\hbar}{2} \left(\begin{array}{cc}
1 & 0\\
0 &  -1
\end{array}
\right)
\end{align}

\subsection{Case of no perturbation $\Omega = 0$}

This is exactly the case of no applied laser fields that we discussed previously. We simply removed the energy offset $E_m = \frac{E_1+E_2}{2}$ and pulled out the factor $\hbar$, such that $\Delta$ measures a frequency. So we have:
\begin{align}
E_1 = E_m+ \frac{\hbar}{2}\Delta\\
E_2 = E_m- \frac{\hbar}{2}\Delta
\end{align}
We typically call $\Delta$ the energy difference between the levels or the \textbf{detuning}.

\subsection{Case of no detuning $\Delta = 0$}

Let us suppose that the diagonal elements are exactly zero. And for simplicity we will also keep $\Omega_y =0$ as it simply complicates the calculations without adding much to the discussion at this stage. The Hamiltonian reads then:
\begin{align}
\hat{H} = \frac{\hbar}{2}\left( \begin{array}{cc} 0  & \Omega\\ \Omega &0 \end{array} \right)
\end{align}

Quite clearly the states $\varphi_{1,2}$ are not the eigenstates of the system anymore. How should the system be described now ? We can once again diagonalize the system and write
\begin{align}
\hat{H}\ket{\varphi_{\pm}} = E_{\pm}\ket{\varphi_\pm}\\
E_{\pm} = \pm\frac{\hbar}{2}\Omega\\
\ket{\varphi_\pm} = \frac{\ket{\varphi_1}\pm\ket{\varphi_2}}{\sqrt{2}}
\end{align}
Two important consequences can be understood from this result:
\begin{enumerate}
\item The coupling of the two states shifts their energy by $\Omega$. This is the idea of level repulsion.
\item The coupled states are a superposition of the initial states.
\end{enumerate}
This is also a motivation the formulation of the 'bare' system for $\Omega = 0$ and the 'dressed' states for the coupled system.